Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-12-01 papers/thesis-kirstie/thesis.tex
use generated figurs
remove figure placement tweaks

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{plot_HardSphere_Potential.pdf}
    \caption{A hard-sphere potential is zero for $r>2R$, and infinity 
    for $r<{2R}$ where R is the radius of a hard sphere (which is 
    approximately 1.225/2 in this example).}
    \label{fig:HardSphere_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential.pdf}
    \caption{Lennard-Jones potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential_2part.pdf}
    \caption{Lennard-Jones potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{WCA_Potential.pdf}
    \caption{WCA potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=3.5cm]{figs/TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{P-T_Diagram.pdf}
    \caption{Conceptual Pressure-Temperature Phase Diagram}
    \label{fig:P-T_Diagram}
  \end{figure}
The pressure can be related to the Helmholtz free energy F, which is minimized 
for a system at fixed temperature, volume and number of particles as the 
entropy of the system and its surroundings is maximized. The negative of 
the partial derivative of the Helmholtz free energy with respect to volume V 
at a fixed temperature T and number of particles N equals the pressure. 
\begin{equation}{P=-\frac{\partial{F}}{\partial{V}}\bigg|_{T,N}}\end{equation}
\noindent Dividing both the Helmholtz free energy and the volume by the 
number of particles, the partial derivative of the Helmholtz free energy 
with respect to volume becomes the partial derivative of the Helmholtz 
free energy per atom, $f$,  with respect to the inverse number density. 
\begin{equation}{P=-\frac{\partial{\frac{F}{N}}}{\partial{\frac{V}{N}}}\bigg|_{T,N} = -\frac{\partial{f}}{\partial{\frac{1}{n}}}\bigg|_{T,N}}\end{equation} 
Thus, the pressure corresponds to the negative of the slope of the curve 
on a plot of the Helmholtz free energy per atom versus the inverse 
density at fixed temperature.

@@

\begin{figure}[h!]
    \centering
     \includegraphics[height=8cm]{figs/MaxwellDTC-Fig1.pdf}
    \caption{Liquid and solid densities at the solid-liquid phase 
    transition are identified using Maxwell's Double Tangent Construction}
    \label{fig:MaxwellDT}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
     \includegraphics[height=8cm]{figs/MaxwellDTC-Fig2.pdf}
    \caption{Pressure is found at point of intersection which occurs 
    when $\mu_L=\mu_S$.}
    \label{fig:GibbsvsP}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{figs/MaxwellDTC-Fig3.pdf}
    \caption{The liquid and solid densities at the phase transition are 
    found from a plot of pressure vs inverse density for both the liquid and the solid.}
    \label{fig:Pvsinvn}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{T-n_Diagram.pdf}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify 
    the number densities of the liquid and the solid during a phase 
    transition. The gray region is where the liquid and the solid coexist, 
    and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure}

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{figs/diagrammic.pdf}
    \caption{Two-pair interactions $f_{ij}f_{kl}$ are shown for N=4 atoms. 
    Interactions between individual pairs of atoms are shown in green. 
    Interactions between pairs of atoms with an atom shared in common 
    are shown in red. At low densities only the interactions shown in 
    green are considered, since atoms are not likely to be clustered.}
    \label{fig:diagrammic}
  \end{figure}

@@

\begin{figure}[h!]

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[height=3.5cm]{PrimitiveCellLightBlue.png}
    \caption{A primitive crystal cell is shown by the shaded parallelepiped.}
    \label{fig:primitivecell}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Gaussian.png}
    \caption{On the left are shown four examples of possible positions 
    that an atom (blue sphere) might have within a cell that has one 
    lattice site (black dot) at the center. A large number of such 
    possibilities would give rise to a Gaussian distribution, 
    as shown on the right.}
    \label{fig:Ensemble_Gaus}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{Gaussian}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Smallcells.png}
    \caption{On the left are shown four examples of possible positions 
    that an atom (blue sphere) might have within a fixed volume 
    containing eight cells. Each cell has one lattice site at the center 
    represented by a black dot. A large number of such possibilities 
    would give rise to the Gaussian distributions shown on the right.}
    \label{fig:Ensemble_Smallcells}
  \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{SameStatPic.png}
    \caption{Front views of a cube with eight smaller cells. The two views 
    show two ways of picturing a fraction of vacancies, $f_v$ of 7/8 which 
    give rise to the same Gaussian distribution statistically, 
    and the same number density.}
    \label{fig:SameStatPic}
  \end{figure}

To implement classical Density Functional Theory, 
a set of number density profiles is generated by varying the Gaussian width 
and the fraction of vacancies at a given combination of temperature and 
number density, as shown by the example in Figure~\ref{fig:Ensemble_vary}.
A homogeneous number density profile is used for a liquid, as shown in 
Figure \ref{fig:homogen_denisty}.
Once again, it is important to note that the number density is the same 
for all these number density profiles $n(\vec{r})$. 
\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{VaryWidthandVacancies.png}
    \caption{Shows an example set of Gaussian distribution number density 
    profiles $n(vec r)$ all with the same number density.
    with the same number density of one atom over the fixed volume.}
    \label{fig:Ensemble_vary}
  \end{figure}  
 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{figs/homogeneous_bold-box.pdf}
    \caption{A homogeneous number density profile $n(\vec{r})$.}
    \label{fig:homogen_denisty}
  \end{figure}  
The Helmholtz free energy $F[n(\vec{r})]$ is calculated for each number 
density profile in the set, and also for the homogeneous number density profile 
characteristic of a liquid. Both the ideal and excess free energies are 
found, and added together to get the total Helmholtz free energy.
According to cDFT, the actual equilibrium Helmholtz free energy at
the given temperature and number density will be the one
that corresponds to the number density profile that minimizes the functional. 
This process is repeated to find the free energies at other combinations 
of temperatures and number densities.

@@

The weight functions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed error function model~\cite{schmidt2000fluid} designed 
to model a steep, soft potential in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha$ and $\Xi$.
The two parameters $\alpha$ and $\Xi$ make the temperature-dependent error 
function potential $V_{erf}(r)$ approximate, in the region of interest, 
the temperature-independent WCA potential which is difficult 
to implement computationally. 
%$\Xi(T)$ is determined by setting the second virial coefficient $B_2$ of 
%the error function potential $V_{erf}(r)$ equal to that of the
%WCA potential, $B_{2erf}(T)=B_{2wca}(T)$ for a given temperature.  
The error function potential emerges from $w_{3}(r)$, and the relationships 
in Equations~\ref{w2_w3_relation} and~\ref{mayerder=w2convolution}.
Using Equation~\ref{w2_w3_relation} repeated here,
\begin{displaymath}
     w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)
\end{displaymath}
and solving for $w_2(r)$
\begin{align}{\frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)}\end{align} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} 
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}
    \frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}
\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{erf}(r)$ is thus 
given by
\begin{align}  \label{eq:VerfMayerfunction}
     f(r)=-\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)\right]
\end{align} 
Combining this result with the definition of the Mayer function 
\begin{align}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{align} 
gives an expression for the for the error function potential  $V(r)=V_{erf}(r)$ 
\begin{equation} \label{eq:Verf}
	V_{erf}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]
\end{equation}

The parameter $\alpha(T)$ is derived by setting 
the error function potential $V_{erf}(r)$ 
equal to the WCA potential given by Equation~\ref{eq:VWCA} at $r=\alpha$. 
\begin{align}
    V_{erf}(\alpha)=V_{WCA}(\alpha)
\end{align}
This gives
\begin{equation}\label{alphaT}\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}\end{equation} 
Figure \ref{fig:alphaXivsT} shows how $\alpha(T)$ varies with temperature 
when $\sigma=1$ and $\epsilon=1$.    
\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{plot_alpha.pdf}
    \caption{Shows the temperature dependence of $\alpha$ vs $k_BT$ 
    for $\sigma=1$ and $\epsilon=1$.}
    \label{fig:alphaXivsT}
  \end{figure}

We determine the value of $\Xi(T)$ at a given temperature $T$,
by setting the second virial coefficient evaluated for the error 
function potential $V_{\operatorname{erf}}(r)$ equal to the second virial 
coefficient evaluated for the WCA potential $V_{WCA}(r)$.
\begin{equation}B_{2\operatorname{erf}}(T) =B_{2WCA}(T)\end{equation}
The second virial coefficient is given by
\begin{equation}B_2=-\frac{1}{2}\int_{Volume}f(\vec{r})d\vec r\end{equation}
Using the Mayer function for the error function potential given by 
Equation~\ref{eq:VerfMayerfunction} we found (see Appendix) the second 
virial coefficient $B_{2}$ for the error function potential $V_{erf}(r)$ 
to be
\begin{equation} \label{eq:B2erf}
	B_{2\operatorname{erf}}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{\operatorname{erf}}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT}. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation} \label{eq:B2wca}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}
The parameter $\Xi(T)$ is found to be the value that makes Equations~\ref{eq:B2erf} 
and \ref{eq:B2wca} equal each other for a given temperature T. 
A plot of $\Xi(T)$ obtained through this method is shown in 
Figure~\ref{fig:xi_fromB2vsT}.
\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $\Xi$ generated from 
    matching the second virial coefficients for $V_{\operatorname{erf}}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:xi_fromB2vsT}
  \end{figure}

Figure \ref{fig:weight_functions} shows a one dimensional view of the 
weight functions $w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance 
along the z-axis. In three dimensions, the weighting functions 
$w_0$, $w_1$, $w_2$ are spherical shells centered at $\vec{r}$, 
and $w_3$ is a solid sphere with an edge that tapers off.
$\Xi$ is related to the width of the weight functions which 
become thicker, or taper off longer as the temperature increases. 
$\alpha$ is related to the radius of the shell, or sphere, and decreases 
as the temperature increases.

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{weight_functions.pdf}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ 
    vary along the z-axis for a reduced temperature of $K_BT=2$.}
    \label{fig:weight_functions}
  \end{figure}

@@

The liquid ideal Helmholtz free energy is computed analytically 
using Equation~\ref{eq:Fideal} 
for a given homogeneous reduced density $n^*$, and reduced temperature $t^*$. 
The crystal ideal Helmholtz free energy is computed computationally 
from Equation~\ref{eq:Fideal-n(r)} with the varying number density profile given by
\begin{align}
  n(|\vec{r}-\vec{R_j}|)=\sum_j{(1-f_v)\frac{e^{-\frac{{|\vec{r}-\vec{R_j}|}^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}}
\end{align}
where $\vec R_j$ is the position vector of the jth lattice site.
The liquid excess Helmholtz free energy is computed analytically  
using SFMT Equations~\ref{eq:Fexfunctional} through \ref{eq:tensorweight-methods} 
with a uniform number density profile, n that does not depend on $\vec r$.

>>>>

\begin{figure}
    \centering
    \includegraphics[height=7cm]{plot_HardSphere_Potential.pdf}
    \caption{A hard-sphere potential is zero for $r>2R$, and infinity 
    for $r<{2R}$ where R is the radius of a hard sphere (which is 
    approximately 1.225/2 in this example).}
    \label{fig:HardSphere_potential}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=7cm]{LJ_Potential.pdf}
    \caption{Lennard-Jones potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=7cm]{LJ_Potential_2part.pdf}
    \caption{Lennard-Jones potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

\begin{figure}
    \centering
    \includegraphics[height=7cm]{WCA_Potential.pdf}
    \caption{WCA potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=3.5cm]{figs/TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=6cm]{figs/P-T_Diagram.pdf}
    \caption{Conceptual Pressure-Temperature Phase Diagram}
    \label{fig:P-T_Diagram}
  \end{figure}
The pressure can be related to the Helmholtz free energy F, which is minimized 
for a system at fixed temperature, volume and number of particles as the 
entropy of the system and its surroundings is maximized. The negative of 
the partial derivative of the Helmholtz free energy with respect to volume V 
at a fixed temperature T and number of particles N equals the pressure. 
\begin{equation}{P=-\frac{\partial{F}}{\partial{V}}\bigg|_{T,N}}\end{equation}
\noindent Dividing both the Helmholtz free energy and the volume by the 
number of particles, the partial derivative of the Helmholtz free energy 
with respect to volume becomes the partial derivative of the Helmholtz 
free energy per atom, $f$,  with respect to the inverse number density. 
\begin{equation}{P=-\frac{\partial{\frac{F}{N}}}{\partial{\frac{V}{N}}}\bigg|_{T,N} = -\frac{\partial{f}}{\partial{\frac{1}{n}}}\bigg|_{T,N}}\end{equation} 
Thus, the pressure corresponds to the negative of the slope of the curve 
on a plot of the Helmholtz free energy per atom versus the inverse 
density at fixed temperature.

@@

\begin{figure}
    \centering
     \includegraphics[height=8cm]{figs/MaxwellDTC-Fig1.pdf}
    \caption{Liquid and solid densities at the solid-liquid phase 
    transition are identified using Maxwell's Double Tangent Construction}
    \label{fig:MaxwellDT}
  \end{figure}

@@

\begin{figure}
    \centering
     \includegraphics[height=8cm]{figs/MaxwellDTC-Fig2.pdf}
    \caption{Pressure is found at point of intersection which occurs 
    when $\mu_L=\mu_S$.}
    \label{fig:GibbsvsP}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[height=8cm]{figs/MaxwellDTC-Fig3.pdf}
    \caption{The liquid and solid densities at the phase transition are 
    found from a plot of pressure vs inverse density for both the liquid and the solid.}
    \label{fig:Pvsinvn}
  \end{figure}

\begin{figure}
    \centering
    \includegraphics[height=6cm]{figs/T-n_Diagram.pdf}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify 
    the number densities of the liquid and the solid during a phase 
    transition. The gray region is where the liquid and the solid coexist, 
    and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[height=7cm]{figs/diagrammic.pdf}
    \caption{Two-pair interactions $f_{ij}f_{kl}$ are shown for N=4 atoms. 
    Interactions between individual pairs of atoms are shown in green. 
    Interactions between pairs of atoms with an atom shared in common 
    are shown in red. At low densities only the interactions shown in 
    green are considered, since atoms are not likely to be clustered.}
    \label{fig:diagrammic}
  \end{figure}

@@

\begin{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[height=3.5cm]{PrimitiveCellLightBlue.png}
    \caption{A primitive crystal cell is shown by the shaded parallelepiped.}
    \label{fig:primitivecell}
  \end{figure}

@@

 \begin{figure}
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Gaussian.png}
    \caption{On the left are shown four examples of possible positions 
    that an atom (blue sphere) might have within a cell that has one 
    lattice site (black dot) at the center. A large number of such 
    possibilities would give rise to a Gaussian distribution, 
    as shown on the right.}
    \label{fig:Ensemble_Gaus}
  \end{figure}

 \begin{figure}
    \centering
    \includegraphics[height=6cm]{Gaussian}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Smallcells.png}
    \caption{On the left are shown four examples of possible positions 
    that an atom (blue sphere) might have within a fixed volume 
    containing eight cells. Each cell has one lattice site at the center 
    represented by a black dot. A large number of such possibilities 
    would give rise to the Gaussian distributions shown on the right.}
    \label{fig:Ensemble_Smallcells}
  \end{figure}

\begin{figure}
    \centering
    \includegraphics[height=2.5cm]{SameStatPic.png}
    \caption{Front views of a cube with eight smaller cells. The two views 
    show two ways of picturing a fraction of vacancies, $f_v$ of 7/8 which 
    give rise to the same Gaussian distribution statistically, 
    and the same number density.}
    \label{fig:SameStatPic}
  \end{figure}

To implement classical Density Functional Theory, 
a set of number density profiles is generated by varying the Gaussian width 
and the fraction of vacancies at a given combination of temperature and 
number density, as shown by the example in Figure~\ref{fig:Ensemble_vary}.
A homogeneous number density profile is used for a liquid, as shown in 
Figure \ref{fig:homogen_denisty}.
Once again, it is important to note that the number density is the same 
for all these number density profiles $n(\vec{r})$. 
\begin{figure}
    \centering
    \includegraphics[height=8cm]{VaryWidthandVacancies.png}
    \caption{Shows an example set of Gaussian distribution number density 
    profiles $n(vec r)$ all with the same number density.
    with the same number density of one atom over the fixed volume.}
    \label{fig:Ensemble_vary}
  \end{figure}  
 \begin{figure}
    \centering
    \includegraphics[height=4cm]{figs/homogeneous_bold-box.pdf}
    \caption{A homogeneous number density profile $n(\vec{r})$.}
    \label{fig:homogen_denisty}
  \end{figure}  
The Helmholtz free energy $F[n(\vec{r})]$ is calculated for each number 
density profile in the set, and also for the homogeneous number density profile 
characteristic of a liquid. Both the ideal and excess free energies are 
found, and added together to get the total Helmholtz free energy.
According to cDFT, the actual equilibrium Helmholtz free energy at
the given temperature and number density will be the one
that corresponds to the number density profile that minimizes the functional. 
This process is repeated to find the free energies at other combinations 
of temperatures and number densities.

@@

\begin{figure}
  \centering
  \includegraphics[height=8cm]{plot_alpha.pdf}
  \caption{Shows the temperature dependence of $\alpha$ vs $k_BT$ 
  for $\sigma=1$ and $\epsilon=1$.}
  \label{fig:alphaXivsT}
\end{figure}
The weight functions $w_{2}(r)$ and $w_{3}(r)$ are constructed using 
Schmidt's proposed error function model~\cite{schmidt2000fluid} designed 
to model a steep, soft potential in which he set
\begin{equation}{w_3(r)=\frac{1}{2}}\left[1-\operatorname{erf}\left(\frac{r-\frac{\sigma}{2}}{\frac{\text{a}}{\sqrt{2}}}\right)\right]\end{equation} 
subject to the boundary conditions $w_3(0)\approx{1}$ 
and $w_3(\infty)=0$. 
Our functional is  created by replacing Schmidt's parameters $\sigma$ 
and $a$ with our temperature dependent parameters $\alpha$ and $\Xi$.
The two parameters $\alpha$ and $\Xi$ make the temperature-dependent error 
function potential $V_{erf}(r)$ approximate, in the region of interest, 
the temperature-independent WCA potential which is difficult 
to implement computationally. 
%$\Xi(T)$ is determined by setting the second virial coefficient $B_2$ of 
%the error function potential $V_{erf}(r)$ equal to that of the
%WCA potential, $B_{2erf}(T)=B_{2wca}(T)$ for a given temperature.  
The error function potential emerges from $w_{3}(r)$, and the relationships 
in Equations~\ref{w2_w3_relation} and~\ref{mayerder=w2convolution}.
Using Equation~\ref{w2_w3_relation} repeated here,
\begin{displaymath}
     w_{3}=\int_{r}^{\infty}{w_{2}(\vec{r})dr}\mbox{~~~~or equivilantly,~~~~}-\frac{\partial{w_3(r)}}{\partial{r}}=w_2(r)
\end{displaymath}
and solving for $w_2(r)$
\begin{align}{\frac{dw_3(r)}{dr}\bigg|_{\infty}-\frac{dw_3(r)}{dr}\bigg|_{r}=w_2(r)}\end{align} 
we get \begin{equation}{ w_2(r)=\frac{\sqrt{2}}{\Xi\sqrt\pi}\exp^{-\left(\frac{r-\frac{\alpha}{2}}{\Xi/\sqrt{2}}\right)^2} }\end{equation} 
Putting $w_2(r)$ into Equation~\ref{mayerder=w2convolution}, shown again below, 
\begin{displaymath}
    \frac{df(r)}{dr}=\int_{-\infty}^{\infty}{w_2(r')w_2(r-r')dr'}
\end{displaymath}
gives
\begin{equation}{\frac{df(r)}{dr}=\frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r-\alpha}{\Xi}\right)^2}}\end{equation} 
which can be integrated to obtain the Mayer function
\begin{equation}{f(r)=\int_{\infty}^r{ \frac{1}{\Xi\sqrt{\pi}}e^{-\left(\frac{r'-\alpha}{\Xi}\right)^2}{dr'}}}\end{equation} 
The Mayer function for the error function potential $V_{erf}(r)$ is thus 
given by
\begin{align}  \label{eq:VerfMayerfunction}
     f(r)=-\frac{1}{2}\left[1-\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)\right]
\end{align} 
Combining this result with the definition of the Mayer function 
\begin{align}f(r)=e^{-\frac{V(r)}{K_BT}}-1\end{align} 
gives an expression for the for the error function potential  $V(r)=V_{erf}(r)$ 
\begin{equation} \label{eq:Verf}
	V_{erf}(r)=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]
\end{equation}  
The parameter $\alpha(T)$ is derived by setting 
the error function potential $V_{erf}(r)$ 
equal to the WCA potential given by Equation~\ref{eq:VWCA} at $r=\alpha$. 
\begin{align}
    V_{erf}(\alpha)=V_{WCA}(\alpha)
\end{align}
This gives
\begin{equation}\label{alphaT}\alpha(T)=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}\end{equation} 
Figure \ref{fig:alphaXivsT} shows how $\alpha(T)$ varies with temperature 
when $\sigma=1$ and $\epsilon=1$.

  \begin{figure}
    \centering
    \includegraphics[height=8cm]{xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $\Xi$ generated from 
    matching the second virial coefficients for $V_{\operatorname{erf}}(r)$ and $V_{WCA}(r)$ 
    at each temperature.}
    \label{fig:xi_fromB2vsT}
  \end{figure}

We determine the value of $\Xi(T)$ at a given temperature $T$,
by setting the second virial coefficient evaluated for the error 
function potential $V_{\operatorname{erf}}(r)$ equal to the second virial 
coefficient evaluated for the WCA potential $V_{WCA}(r)$.
\begin{equation}B_{2\operatorname{erf}}(T) =B_{2WCA}(T)\end{equation}
The second virial coefficient is given by
\begin{equation}B_2=-\frac{1}{2}\int_{Volume}f(\vec{r})d\vec r\end{equation}
Using the Mayer function for the error function potential given by 
Equation~\ref{eq:VerfMayerfunction} we found (see Appendix) the second 
virial coefficient $B_{2}$ for the error function potential $V_{erf}(r)$ 
to be
\begin{equation} \label{eq:B2erf}
	B_{2\operatorname{erf}}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{\operatorname{erf}}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]
\end{equation}
where $\alpha(T)$ is given by Equation~\ref{alphaT}. Similarly, 
$B_{2WCA}$ can be found computationally from 
\begin{equation} \label{eq:B2wca}
	B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} 
\end{equation}
The parameter $\Xi(T)$ is found to be the value that makes Equations~\ref{eq:B2erf} 
and \ref{eq:B2wca} equal each other for a given temperature T. 
A plot of $\Xi(T)$ obtained through this method is shown in 
Figure~\ref{fig:xi_fromB2vsT}.

\begin{figure}
  \centering
  \includegraphics[height=8cm]{weight_functions.pdf}
  \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ 
  vary along the z-axis for a reduced temperature of $K_BT=2$.}
  \label{fig:weight_functions}
\end{figure}
Figure \ref{fig:weight_functions} shows a one dimensional view of the 
weight functions $w_0$, $w_1$, $w_2$, $w_3$ as they vary with distance 
along the z-axis. In three dimensions, the weighting functions 
$w_0$, $w_1$, $w_2$ are spherical shells centered at $\vec{r}$, 
and $w_3$ is a solid sphere with an edge that tapers off.
$\Xi$ is related to the width of the weight functions which 
become thicker, or taper off longer as the temperature increases. 
$\alpha$ is related to the radius of the shell, or sphere, and decreases 
as the temperature increases.

@@

The liquid ideal Helmholtz free energy is computed analytically 
using Equation~\ref{eq:Fideal} 
for a given homogeneous reduced density $n^*$, and reduced temperature $t^*$. 
The crystal ideal Helmholtz free energy is computed computationally 
from Equation~\ref{eq:Fideal-n(r)} with the varying number density profile given by
\begin{align}
  n(|\vec{r}-\vec{R_j}|)=\sum_j{(1-f_v)\frac{e^{-\frac{{|\vec{r}-\vec{R_j}|}^2}{2{\sigma}^2}}}{\left(\sqrt{2\pi}\sigma\right)^3}}
\end{align}
where $\vec R_j$ is the position vector of the jth lattice site.
The liquid excess Helmholtz free energy is computed analytically  
using SFMT Equations~\ref{eq:Fexfunctional} through \ref{eq:tensorweight-methods} 
with a uniform number density profile, n that does not depend on $\vec r$. 
\begin{figure}
  \centering
  (a) \includegraphics[height=7cm]{figs/weightandGauss1.pdf}\\
  (b) \includegraphics[height=7cm]{figs/weightandGauss2.pdf}
  \caption{(a) A Gaussian distribution about a lattice site located at 
  $\vec R$ is shown in blue, and a cross-sectional 
  view of $w_2$ centered at $\vec r~'$ is shown in purple.
  (b) An alternative way of viewing the top figure, where 
  the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
  and fixed in place as $\vec r~' - \vec R$
  varies randomly with a probability according to a Gaussian distribution.}
\label{fig:GaussandW2_actual}
\end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[height=7cm]{figs/weightandGauss2.pdf}
%   \caption{An alternative way of viewing Figure~\ref{fig:GaussandW2_actual} where 
%   the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
%   and fixed in place as $\vec r~' - \vec R$
%   varies randomly with a probability according to a Gaussian distribution.} 
% \label{fig:GaussandW2_thinkas}
% \end{figure}
